\plaintitle

### 2017-04-25 statistical-quorum.tex
Added table for example.

>>>>

Even if voting turnout has reached legally required quorum, it is still a question how to evaluate if
the turnout is high enough to find results legitimate.
As an example we can look at two recent votes, Brexit, a 2016 referendum for United Kingdom's withdrawal
from the European Union, and popular vote in 2016 USA presidential elections, as seen in Table~\ref{tab:example}.

\begin{table*}
  \centering
  \begin{tabular}{l r r r r r r r}
    {\small\textit{Vote}} & \multicolumn{2}{r}{\small \textit{First option}} & \multicolumn{2}{r}{\small \textit{Second option}} & {\small \textit{Total eligible voters}} & {\small \textit{Turnout}} & {\small \textit{Statistical quorum}} \\
    \midrule
    Brexit & 17,410,742 & $51.9\%$ & 16,141,241 & $48.1\%$ & 46,500,001 & $72.2\%$ & \\
    Presidential elections & 62,984,825 & $48.9\%$ & 65,853,516 & $51.1\%$ & 250,055,734 & $51.5\%$ & \\
  \end{tabular}
  \caption{Votes cast in Brexit, a 2016 referendum for United Kingdom's withdrawal from the European Union,
  and 2016 USA presidential elections, popular vote. Simplified to only two options and without invalid votes.}\label{tab:example}
\end{table*}

%for example: trump and brexit
%
%we define measure of creditibility, statistical quorm, to evaluate this
%
%the easiest is to claim that results are legitimate becaue people had an option to participate, and they decided not to
%
%but what if they didn't have time to participate? or determined that they are not informed enough to participate?
%
%instead of trying to increase participation, we can look at participation as it is, and try to utilize it better
%
%we can use the same statistical quorum to direct collective attention to decisions which require more participation
%and away from those which do not
%
%instead of requiring same arbitirary high static quorum for all decisions, we can require same creditibility, which
%depends on votes made define if enough members participated
%
%Example
